---
title: "Parallelization Simulation"
author: "Jonathan Rosenblatt"
date: "1/1/2015"
output: pdf_document
---
```{r Initializing}
library(InformationAndInference)
ms <- c(1e1, 1e2)
p <- 1e2
replications <- 2L
kappas <- seq(2^-6, 2^-2, length.out = 2)
```


```{r MakeConfiguration}
configuration <- makeConfiguration() 
```


## OLS

Now computing the ratio of $l_2$ norm of errors between estimtors:
```{r}
.getMSE <- function(kappa) getMSERegression_ms(replications, kappa, p, ms, my.ols, coefs.ols)
MSEs_ms.0 <- kappas %>% lapply(.getMSE)
```

```{r}
cl <- makeCluster(detectCores()-1)
clusterEvalQ(cl, {
  source('libraries.R')
  source('utility.R')
  source('utility_fixed_p_vary_m.R')
  })
exporting <- c('p', 'ms','kappas','replications', '.getMSE', 'my.ols', 'coefs.ols')
clusterExport(cl, exporting )
MSEs_ms.0 <- parLapplyLB(cl, kappas, .getMSE)
stopCluster(cl)
```


```{r plot_1, eval=FALSE, echo=FALSE}
plotMSE_ms(MSEs_ms.0, p, kappas, replications , "Squared")
```




## Huber Loss
```{r Huber, eval=FALSE, echo=FALSE}
for(i in 1:4) {
  compareParallelizeRegression_ms(p, kappa =2^-i, ms, my.huber, coefs.huber)
  }
```


Now computing the ratio of $l_2$ norm of errors between estimtors:
```{r}
.getMSE <- function(kappa) getMSERegression_ms(
  replications, kappa, p, ms, my.huber, coefs.huber)
# MSEs.2 <- kappas %>% lapply(.getMSE)

cl <- makeCluster(detectCores()-1)
clusterEvalQ(cl, {
  source('libraries.R')
  source('utility.R')
  source('utility_fixed_p_vary_m.R')
  })
exporting <- c('p', 'ms','kappas','replications', '.getMSE', 
               'my.huber', 'coefs.huber')
clusterExport(cl, exporting)
MSEs_ms.1 <- parLapplyLB(cl, kappas, .getMSE)
stopCluster(cl)
```

```{r plot_2, eval=FALSE, echo=FALSE}
plotMSE_ms(MSEs_ms.1, p, kappas, "Huber")
```



## Absolute loss regression:
```{r Absolute_loss, eval=FALSE, echo=FALSE}
for(i in 1:4) {
  compareParallelizeRegression_ms(p, kappa =2^-i, ms, 
                                  my.absolute, coefs.absolute)
  }
```


Now computing the ratio of MSEs between estimtors:
```{r, cache=TRUE}
.getMSE <- function(kappa) getMSERegression_ms(
  replications, kappa, p, ms, my.absolute, coefs.absolute)
# MSEs.3 <- kappas %>% lapply(.getMSE)

cl <- makeCluster(detectCores()-1)
clusterEvalQ(cl, {
  source('libraries.R')
  source('utility.R')
  source('utility_fixed_p_vary_m.R')
  })
exporting <- c('p', 'ms','kappas','replications', '.getMSE',
               'my.absolute', 'coefs.absolute')
clusterExport(cl, exporting )
MSEs_ms.3 <- parLapplyLB(cl, kappas, .getMSE)
stopCluster(cl)
```

```{r plot_3, eval=FALSE, echo=FALSE}
plotMSE_ms(MSEs_ms.3, p, kappas, "Absolute")
```




## Logistic Regression
```{r Logistic, eval=FALSE, echo=FALSE}
for(i in 2:5) {
  compareParallelizeClassification_ms(p, kappa =2^-i, ms, 
                                      my.logistic, coefs.logistic)
  }
```


Now computing the ratio of $l_2$ norm of errors beween estimtors:
```{r}
.getMSE <- function(kappa) getMSEClassification_ms(
  replications, kappa, p, ms, my.logistic, coefs.logistic)
# MSEs.5 <- kappas %>% lapply(.getMSE)

cl <- makeCluster(detectCores()-1)
clusterEvalQ(cl, {
  source('libraries.R')
  source('utility.R')
  source('utility_fixed_p_vary_m.R')
  })
exporting <- c('p', 'ms','kappas','replications', '.getMSE', 
               'my.logistic', 'coefs.logistic')
clusterExport(cl, exporting)
MSEs_ms.5 <- parLapplyLB(cl, kappas, .getMSE)
stopCluster(cl)
```

```{r plot_4}
plotMSE_ms(MSEs_ms.5, p, kappas, replications, "Logistic", y.lim = c(0,20))
```




```{r all_plots}
#save.image(file = 'RData_files/classic_asymptotic_image.RData')
#load(file = 'RData_files/classic_asymptotic_image.RData')

plot.1 <- plotMSE_ms(MSEs_ms.0, p, kappas , "(a) Squared")
plot.2 <- plotMSE_ms(MSEs_ms.1, p, kappas, "(b) Huber")
plot.3 <- plotMSE_ms(MSEs_ms.3, p, kappas, "(c) Absolute")
plot.4 <- plotMSE_ms(MSEs_ms.5, p, kappas, "(d) Logistic", y.lim = c(1,20))

# directory <- "~/Dropbox/Boaz Shared/Parallelize/Simulation/Output/"
# the.file <-paste(directory, "clasic_asymptotics_1.pdf", sep='')
# pdf(file=the.file, onefile = FALSE, paper = "special", width=8, height=8)
grid.arrange(plot.1, plot.2, plot.3, plot.4, ncol=2)
# dev.off()
```


## Misspecified
```{r misspecified, eval=FALSE, echo=FALSE}
# link <- function(x) tanh(x+10)/10
# for(i in 1:4) {
#   compareParallelizeRegression_ms(p , kappa =2^-i, ms, 
#                                   my.ols, coefs.ols, 
#                                   link=link, sigma = 0 )
#   }
```


Now computing the ratio of $l_2$ norm of errors between estimtors:
```{r, eval=FALSE, echo=FALSE}
.getMSE <- function(kappa) getMSERegression_ms(replications, kappa, p, ms, my.ols, coefs.ols, link, sigma=10)
## MSEs_ms.0 <- kappas %>% lapply(.getMSE)
```

```{r, eval=FALSE, echo=FALSE}
# cl <- makeCluster(detectCores()-1)
# clusterEvalQ(cl, {
#   source('utility.R')
#   source('utility_vary_m.R.R')  
#   })
# exporting <- c('p', 'ms','kappas','replications', '.getMSE', 'my.ols', 'coefs.ols', 'link')
# clusterExport(cl, exporting )
# MSEs_ms_misspecified.0 <- parLapplyLB(cl, kappas, .getMSE)
# stopCluster(cl)
```


```{r , eval=FALSE, echo=FALSE}
# plotMSE_ms(MSEs_ms_misspecified.0, p, kappas , "Squared")
```

